\Large \bf SIRIUS: A Revolutionary Approach to I/O and Storage for Exascale Scientific Computing

### 2016-03-07 papers/2016-HotStorage/paper.tex
fixed some formatting

\noindent\textbf{Quality of Service} deadlines are important for driving how
much time is spent performing IO. At the same time, data quality must be
maintained at a sufficient level for the resulting science to be possible.
The system must offer a way for an end-user to negotiate with the system for
trading off between time spent in IO and the amount of data written or read.
Part of that tradeoff will be increased or reduced data quality, depending on
the system. For example, when data is written, a few different forms may be
output given sufficient space and time. One may be every fourth element
across a regular mesh reduces the data size to $1/64^th$ the full data set.
Further dividing that using byte-splitting can reduce it by another 75\%. For
quick overviews to search data sets, this reduced form can be sufficient
driving which data sets should be investigated in more detail. The key driving
factor is time. The applicaiton scientist can read 0.4\% of the full data
volume with a similar time reduction. SIRIUS will offer a negotiation process
to read any data.

First, a user will request a particular variable and timesetp. SIRIUS will
return a table similar to Table~\ref{tab:results}. For a given variable ``A'',
the end-user can then select the data quality and approximate reading time for
the operation. In this case, there are 5 options for obtaining the whole data
set (1/2/3/4, 5/6, 7/8, 9, 10). The first four represent a spatial and byte
split, 5/6 represent just strided writing, 7/8 represent just a byte-split, 9
represents a wavelet compressed version, and 10 is the full precision data.
The user would specify to read a particular data instance that would proceed
normally.  Quality of Service soft guarantees specified as part of the request
will result in SIRIUS allocating soft bandwidth reservations to meet the
request.

>>>>

\noindent\textbf{Quality of Service} deadlines are important for driving how
much time is spent performing IO. At the same time, data quality must be
maintained at a sufficient level for the resulting science to be possible.
The system must offer a way for an end-user to negotiate with the system for
trading off between time spent in IO and the amount of data written or read.
Part of that tradeoff will be increased or reduced data quality, depending on
the system. For example, when data is written, a few different forms may be
output given sufficient space and time. One may be every fourth element
across a regular mesh reduces the data size to $1/64^{th}$ the full data set.
Further dividing that using byte-splitting can reduce it by another 75\%. For
quick overviews to search data sets, this reduced form can be sufficient
driving which data sets should be investigated in more detail. The key driving
factor is time. The applicaiton scientist can read 0.4\% of the full data
volume with a similar time reduction. SIRIUS will offer a negotiation process
to read any data.

First, a user will request a particular variable and timesetp. SIRIUS will
return a table similar to Table~\ref{tab:results}. For a given variable ``A'',
the end-user can then select the data quality and approximate reading time for
the operation. In this case, there are 5 options for obtaining the whole data
set (1/2/3/4, 5/6, 7/8, 9, 10). The first four represent a spatial and byte
split, 5/6 represent just strided writing, 7/8 represent just a byte-split, 9
represents a wavelet compressed version, and 10 is the full precision data.
The user would specify to read a particular data instance that would proceed
normally.  Quality of Service soft guarantees specified as part of the request
will result in SIRIUS allocating soft bandwidth reservations to meet the
request. While some of the error rates seem to render the data unusable,
consider a 3000x3000x3000 simulation domain. That would yield a 27 gigapixel
image should all of the data be used. Visualization will already radically
reduce the data sizes to make usable visualizations that work on a standard
display. A 99\% reduction would yield a 270 megapixel image--still quite large.
